Using HMMs for pre-snap coverage detection

### 2024-11-22 submission.Rmd
.

#### 1. Pre-Motion Analysis
We train a model to predict whether the defense plays a man- or zone coverage scheme. The 
model uses the previously described features, blablabla

#### 2. HMM Analysis
We model the movements of defensive players during the phase of pre-snap motion within a hidden Markov framework, in which the underlying states represent the offensive players to be guarded (see Franks et al., 2015 for a similar approach in basketball).

@@

>>>>

#### 1. Pre-Motion Analysis
We train a model to predict whether the defense plays a man- or zone coverage scheme. The 
model uses the previously described features, blablabla and as observations information from those plays without pre-snap motion and information until the first motion for plays with motion.

#### 2. HMM Analysis
We model the movements of defensive players during the phase of pre-snap motion within a hidden Markov framework, in which the underlying states represent the offensive players to be guarded (see Franks et al., 2015 for a similar approach in basketball). In contrast to Groom et al., 2024, who enforce a state to proxy zone coverage during corner kicks in soccer, we cannot proceed similarly as the classical coverage zones in American football will only be covered post-snap. To remediate this, we derive the decision of man- or zone coverage from the number of switches for individual players. In particular, a low number of switches when offensive players are in motion indicates man coverage whereas a higher number indicates zone coverage.

@@

*Groom S, Morris D, Anderson L, Wang S (2024). Modeling Defensive Dynamics in Football: A Hidden Markov Model-Based Approach for Man-Marking and Zonal Defending Corner Analysis. The 2nd International Workshop on Intelligent Technologies for Precision Sports Science
